Illustrating Text

### 2015-12-10 paper/paper.tex
Mostly done. Need to write related work section and add data produced by code

\section{Future Work}
-- better datasets (particularly for images)
-- more complex analysis of images
-- break down of images into features and feature groups

\subsection{Datasets}
Future work needs access to a larger set of images annotated with keywords and phrases. It may be necessary to mine 
for the images and annotations specifically or to crowd source the annotations of mined images. But, it is achievable 
and may provide the results we wished to achieve. One issue we found with google is that the search, provided with two 
words that are nearly identical in meaning, does not provide nearly identical results. Ideally images would have 
similar ranking in a search for words with a similar meaning. We went in expecting there to be a large reuse of images 
between people of different language groups, but our observations now point us in a different direction.

@@

\subsection{Image Analysis and Partitioning of Image Sets}
A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find 
features and feature-groups within an image. Using features and feature-groups we may be able to find which features 
or feature-groups relate to each keyword or keyword-set and pick images based on this. This step is already improved 
if we are able to match multiple modifications of a single image and throwing away the modified versions. Looking at 
an image on a feature basis allows us to generate a better set of images that represent the keywords better.

\subsection{Illustration}
-- Composite Images based on keywords
-- Exploration of culturally ambiguous collages (Left-to-Right Right-to-Left)
-- Image Modification based Salience and Computer Vision

\end{document}

>>>>

\section{Future Work}
\subsection{Datasets}
Future work needs access to a larger set of images annotated with keywords and phrases. It may be necessary to mine 
for the images and annotations specifically or to crowd source the annotations of mined images. But, it is achievable 
and may provide the results we wished to achieve. One issue we found with google is that the search, provided with two 
words that are nearly identical in meaning, does not provide nearly identical results. Ideally images would have 
similar ranking in a search for words with a similar meaning. We went in expecting there to be a large reuse of images 
between people of different language groups, but our observations now point us in a different direction.

@@

\subsection{Image Analysis and Partitioning of Image Sets}
A possible extension of this stage would be to incorporate machine learning and computer vision to be able to find 
features and feature-groups within an image. Using features and feature-groups we may be able to find which features 
or feature-groups relate to each keyword or keyword-set and pick images based on this. This step is already improved 
if we are able to match multiple modifications of a single image and throwing away the modified versions. Looking at 
an image on a feature basis allows us to generate a better set of images that represent the keywords better and means 
that we possibly won't need to have as large of a database of images with similar keyword/phrase annotations.
\paragraph{}
Learning to relate features and feature-groups to keywords and keyphrases can be done independently for each language. 
It may be possible to completely get around a need for a single database of images with keyword/phrase annotations 
for all languages. This would be the best modification to our project and product the best results. One of the biggest 
problems is the database for the images.

\subsection{Illustration}
The step of creating the illustration can be modified in a number of ways. The best method likely varies based on what 
you want to use the results for. For language learning and depending on the text size, it is probably best to either 
find a single image that is representitive of the salient set it represents or to be able to combine the images or 
features related to the keywords into an image. In some cases it probably would be best to have a series of images 
to represent a meaning. Illustrating certain actions would probably require multiple images to be accuratley 
illustrated.
\end{document}
